---
title: "arima_forecasting"
author: "Mihkmihk"
date: "2024-01-30"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(forecast)
library(timeSeries)
library(tseries)
library(fpp2)
library(lubridate)
library(stats)
library(dplyr)

# Leaf Blight, Brown spot, BLSB
disease_forecast_csv <- 
  read_csv("Mean Monthly Disease Percent Incidence.csv")

# FAW, Armyworm, Earworm
pest_forecast_data <- 
  read_csv("pests_forecast_dataset.csv")

# FAW
faw_ts_data <- ts(pest_forecast_data$`Fall Armyworm`, 
                  start = c(2020, 5), 
                  end = c(2023, 7),
                  frequency = 12)

# Earworm
earworm_ts_data <- ts(pest_forecast_data$Earworm, 
                  start = c(2020, 5), 
                  end = c(2023, 7),
                  frequency = 12)

# Armyworm
armyworm_ts_data <- ts(pest_forecast_data$Armyworm, 
                  start = c(2020, 5), 
                  end = c(2023, 7),
                  frequency = 12)

# Leaf Blight
blight_ts_data <- ts(disease_forecast_csv$leafblight, 
                  start = c(2020, 5), 
                  end = c(2023, 7),
                  frequency = 12)

# Brown Spot
brown_ts_data <- ts(disease_forecast_csv$brownspot, 
                  start = c(2020, 5), 
                  end = c(2023, 7),
                  frequency = 12)

# BLSB
blsb_ts_data <- ts(disease_forecast_csv$blsb, 
                  start = c(2020, 5), 
                  end = c(2023, 7),
                  frequency = 12)



months_vector <- c(as.Date("2020-05-01"),
               seq(from = as.Date("2020-06-01"), 
                   to = as.Date("2023-06-01"),
                 by = "month"),
               as.Date("2023-07-01")) %>% as.array()


forecast_months_vector <- c(as.Date("2023-08-01"),
               seq(from = as.Date("2023-09-01"), 
                   to = as.Date("2025-06-01"),
                 by = "month"),
               as.Date("2025-07-01")) %>% as.array()

months_break <- c(as.Date("2020-05-01"),
               seq(from = as.Date("2020-08-01"), 
                   to = as.Date("2025-08-01"),
                 by = "month"),
               as.Date("2025-07-01"))

# # ndiffs function to check how many differences 
# ndiffs(faw_ts_data) # 0
# ndiffs(earworm_ts_data) # 0
# ndiffs(armyworm_ts_data) # 1
# ndiffs(blight_ts_data) # 0
# ndiffs(brown_ts_data) # 1
# ndiffs(blsb_ts_data) # 0



# # nsdiffs function to check how many 
# # seasonal differences required
# nsdiffs(faw_ts_data) # 0
# nsdiffs(earworm_ts_data) # 0
# nsdiffs(armyworm_ts_data) # 0
# nsdiffs(blight_ts_data) # 0
# nsdiffs(brown_ts_data) # 0
# nsdiffs(blsb_ts_data) # 0



color_diseases <- c("chartreuse3", "deepskyblue2", "chocolate2")
color_labels <- c("Banded Leaf and Sheath Blight",
                  "Brown Spot", 
                  "Leaf Blight")

faw_ts_data_color <- "chocolate2"
armyworm_ts_data_color <- "chartreuse3"
earworm_ts_data_color <- "deepskyblue2"

blsb_ts_data_color <- "chartreuse3"

plot_title_size <- 12

```


```FAW Forecasting ARIMA``
```{r}
adf.test(faw_ts_data, alternative = "stationary", k=0)

faw_auto_arima_model <- 
  auto.arima(faw_ts_data, 
             d = 0,
             D = 0,
             stepwise = FALSE,
             approximation = FALSE)
print(summary(faw_auto_arima_model))
checkresiduals(faw_auto_arima_model)


faw_forecast <- forecast(faw_auto_arima_model, 
                              level = c(95),
                              h = 2 * 12)

autoplot(faw_forecast, 
         y = "FAW Percent Incidence", 
         x = "Years")


faw_df <- 
  tibble(
    months = months_vector,
    faw_percent_incidence = array(faw_ts_data),
    faw_lo_mean = NULL,
    faw_up_mean = NULL
  )


faw_forecast_df <- 
  tibble(
    months = forecast_months_vector,
    faw_forecast_percent_incidence = faw_forecast$mean,
    faw_lo_mean = faw_forecast$lower[,"95%"],
    faw_up_mean = faw_forecast$upper[,"95%"]
  )

faw_arima_data <-
  faw_df %>% full_join(faw_forecast_df, by = c("months"))


# annotate("label", x = 24, y = 25,
#              label = "FAW May 2020 - July 2023 Percent Incidences",
#              parse = TRUE) +
#     

faw_arima_data %>%
  ggplot(aes(x = months, y = faw_percent_incidence)) +
  geom_line(color = "chocolate2", alpha = 2, size = 2) +
  annotate("label",
           x = as.Date("2021-04-01"), 
           y = 2.5,
           label = "FAW Percent Incidences \n May 2020 - July 2023",
           color = "chocolate4", size = 5, fill = "floralwhite")+ 
  geom_line(aes(y = faw_forecast_percent_incidence),
            color = "firebrick", alpha = 3, size = 2.2) +
  annotate("text",
           x = as.Date("2024-09-01"), 
           y = 17,
           label = "FAW Forecast Incidences \n Aug 2023 - July 2025",
           color = "brown4", size = 5) +
  geom_ribbon(aes(ymin = 0, 
                  ymax = faw_up_mean),
              alpha = 0.1,
              fill = "orangered") +
  scale_y_continuous(
    breaks = seq(0, 28, 0.75)) +
  labs(x = "Planting Months",
       y = "FAW Percent Incidences",
       title = "FAW Percent Incidences and Forecast") +
  
  scale_x_date(date_labels = format("%b-%Y"),
               date_breaks = "1 month",
               limits = c(min(months_break), max(months_break))) +
  theme(
    plot.title.position = "panel",
    plot.title = element_text(margin = margin(0.1, 0.2, 1.2, 0.2, "cm"),
                              hjust = 0.5,
                              vjust = -119,
                              size = plot_title_size + 5),
    plot.margin = margin(0, 0.1, 1.22, 0.2, "cm"),
    aspect.ratio = 0.35,
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "gray96"),
    axis.text.y = element_text(size = 10,
                               color = "black",
                               face = "plain",
                               vjust = 0.25,
                               margin = margin(b = 1)), 
    axis.text.x = element_text(margin = margin(b = 1),
                               angle = 90, 
                               vjust = 0.5, 
                               size = 12),
    axis.title = element_text(margin = margin(t = 1.3),
                              size = 14)
  )
ggsave("FAW SARIMA Data and Forecast.png", 
       dpi = 150, height = 6, width = 12)
```

```Armyworm Forecasting ARIMA``
```{r}
adf.test(armyworm_ts_data, alternative = "stationary", k=0)

armyworm_auto_arima_model <- 
  auto.arima(armyworm_ts_data, 
             d = 0, 
             D = 0,
             stepwise = FALSE,
             approximation = FALSE)
print(summary(armyworm_auto_arima_model))
checkresiduals(armyworm_auto_arima_model)


armyworm_forecast <- forecast(armyworm_auto_arima_model, 
                         level = c(95),
                         h = 2 * 12)

autoplot(armyworm_forecast, 
         y = "Armyworm Percent Incidence", 
         x = "Years")


armyworm_df <- 
  tibble(
    months = months_vector,
    armyworm_percent_incidence = array(armyworm_ts_data),
    armyworm_lo_mean = NULL,
    armyworm_up_mean = NULL
    )


armyworm_forecast_df <- 
  tibble(
    months = forecast_months_vector,
    armyworm_forecast_percent_incidence = armyworm_forecast$mean,
    armyworm_lo_mean = armyworm_forecast$lower[,"95%"],
    armyworm_up_mean = armyworm_forecast$upper[,"95%"]
    )

armyworm_arima_data <-
  armyworm_df %>% full_join(armyworm_forecast_df, by = c("months"))


# annotate("label", x = 24, y = 25,
#              label = "Armyworm May 2020 - July 2023 Percent Incidences",
#              parse = TRUE) +
#     

armyworm_arima_data %>%
    ggplot(aes(x = months, y = armyworm_percent_incidence)) +
    geom_line(color = "chartreuse3", alpha = 2, size = 2) +
    annotate("label",
           x = as.Date("2021-12-01"), 
           y = 7,
           label = "Armyworm Percent Incidences \n May 2020 - July 2023",
           color = "darkolivegreen", size = 5, fill = "floralwhite")+ 
    geom_line(aes(y = armyworm_forecast_percent_incidence),
              color = "lightseagreen", alpha = 3, size = 2.2) +
    geom_ribbon(aes(ymin = 0, 
                    ymax = armyworm_up_mean),
                    alpha = 0.1,
                    fill = "darkolivegreen1") +
    annotate("text",
           x = as.Date("2024-09-01"), 
           y = 6.5,
           label = "Armyworm Forecast Incidences \n Aug 2023 - July 2025",
           color = "forestgreen", size = 5) +
    scale_y_continuous(
               breaks = seq(0, 22, 0.75)) +
    labs(x = "Planting Months",
         y = "Armyworm Percent Incidences",
         title = "Armyworm Percent Incidences and Forecast") +
  
    scale_x_date(date_labels = format("%b-%Y"),
                 date_breaks = "1 month",
                 limits = c(min(months_break), max(months_break))) +
    theme(
          plot.title.position = "panel",
          plot.title = element_text(margin = margin(0.1, 0.2, 1.2, 0.2, "cm"),
                                                    hjust = 0.5,
                                                    vjust = -119,
                                    size = plot_title_size + 5),
          plot.margin = margin(0, 0.1, 1.22, 0.2, "cm"),
          aspect.ratio = 0.35,
          strip.background = element_blank(),
          strip.placement = "outside",
          panel.background = element_rect(fill = NA),
          panel.grid.major = element_line(colour = "gray96"),
          axis.text.y = element_text(size = 10,
                                   color = "black",
                                   face = "plain",
                                   vjust = 0.25,
                                   margin = margin(b = 1)), 
          axis.text.x = element_text(margin = margin(b = 1),
                                     angle = 90, 
                                     vjust = 0.5, 
                                     size = 12),
          axis.title = element_text(margin = margin(t = 1.3),
                                    size = 14)
          )
ggsave("Armyworm SARIMA Data and Forecast.png", 
       dpi = 150, height = 6, width = 12)

  
```

```Earworm Forecasting ARIMA``
```{r}
adf.test(earworm_ts_data, alternative = "stationary", k=0)

earworm_auto_arima_model <- 
  auto.arima(earworm_ts_data, 
             d = 0,
             D = 0,
             stepwise = FALSE,
             approximation = FALSE)
print(summary(earworm_auto_arima_model))
checkresiduals(earworm_auto_arima_model)


earworm_forecast <- forecast(earworm_auto_arima_model, 
                              level = c(95),
                              h = 2 * 12)

autoplot(earworm_forecast, 
         y = "Earworm Percent Incidence", 
         x = "Years")


earworm_df <- 
  tibble(
    months = months_vector,
    earworm_percent_incidence = array(earworm_ts_data),
    earworm_lo_mean = NULL,
    earworm_up_mean = NULL
  )


earworm_forecast_df <- 
  tibble(
    months = forecast_months_vector,
    earworm_forecast_percent_incidence = earworm_forecast$mean,
    earworm_lo_mean = earworm_forecast$lower[,"95%"],
    earworm_up_mean = earworm_forecast$upper[,"95%"]
  )

earworm_arima_data <-
  earworm_df %>% full_join(earworm_forecast_df, by = c("months"))


# annotate("label", x = 24, y = 25,
#              label = "Earworm May 2020 - July 2023 Percent Incidences",
#              parse = TRUE) +
#     

earworm_arima_data %>%
  ggplot(aes(x = months, y = earworm_percent_incidence)) +
  geom_line(color = "deepskyblue", alpha = 2, size = 2)  +
  annotate("label",
           x = as.Date("2022-01-01"), 
           y = 7.5,
           label = "Earworm Percent Incidences \n May 2020 - July 2023",
           color = "dodgerblue4", size = 4, fill = "floralwhite")+ 
  geom_line(aes(y = earworm_forecast_percent_incidence),
            color = "navyblue", alpha = 3, size = 2.2) +
  annotate("text",
           x = as.Date("2024-09-01"), 
           y = 6,
           label = "Earworm Forecast Incidences \n Aug 2023 - July 2025",
           color = "navyblue", size = 5)+
  geom_ribbon(aes(ymin = 0, 
                  ymax = earworm_up_mean),
              alpha = 0.1,
              fill = "lightskyblue1") +
  scale_y_continuous(
    breaks = seq(0, 10, 0.25)) +
  labs(x = "Planting Months",
       y = "Earworm Percent Incidences",
       title = "Earworm Percent Incidences and Forecast") +
  
  scale_x_date(date_labels = format("%b-%Y"),
               date_breaks = "1 month",
               limits = c(min(months_break), max(months_break))) +
  theme(
    plot.title.position = "panel",
    plot.title = element_text(margin = margin(0.1, 0.2, 1.2, 0.2, "cm"),
                              hjust = 0.5,
                              vjust = -119,
                              size = plot_title_size + 5),
    plot.margin = margin(0, 0.1, 1.22, 0.2, "cm"),
    aspect.ratio = 0.35,
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "gray96"),
    axis.text.y = element_text(size = 10,
                               color = "black",
                               face = "plain",
                               vjust = 0.25,
                               margin = margin(b = 1)), 
    axis.text.x = element_text(margin = margin(b = 1),
                               angle = 90, 
                               vjust = 0.5, 
                               size = 12),
    axis.title = element_text(margin = margin(t = 1.3),
                              size = 14)
  )
ggsave("Earworm SARIMA Data and Forecast.png", 
       dpi = 150, height = 6, width = 12)
```

```Leaf Blight Forecasting ARIMA``
```{r}
adf.test(blight_ts_data, alternative = "stationary", k=0)

blight_auto_arima_model <- 
  auto.arima(blight_ts_data, 
             d  = 1,
             D = 0,
             stepwise = FALSE,
             approximation = FALSE)
print(summary(blight_auto_arima_model))
checkresiduals(blight_auto_arima_model)


blight_forecast <- forecast(blight_auto_arima_model, 
                              level = c(95),
                              h = 2 * 12)

autoplot(blight_forecast, 
         y = "Leaf Blight Percent Incidence", 
         x = "Years")


blight_df <- 
  tibble(
    months = months_vector,
    blight_percent_incidence = array(blight_ts_data),
    blight_lo_mean = NULL,
    blight_up_mean = NULL
  )


blight_forecast_df <- 
  tibble(
    months = forecast_months_vector,
    blight_forecast_percent_incidence = blight_forecast$mean,
    blight_lo_mean = blight_forecast$lower[,"95%"],
    blight_up_mean = blight_forecast$upper[,"95%"]
  )

blight_arima_data <-
  blight_df %>% full_join(blight_forecast_df, by = c("months"))


# annotate("label", x = 24, y = 25,
#              label = "Leaf Blight May 2020 - July 2023 Percent Incidences",
#              parse = TRUE) +
#     

blight_arima_data %>%
  ggplot(aes(x = months, y = blight_percent_incidence)) +
  geom_line(color = "chocolate2", alpha = 2, size = 1.8) +
  annotate("label",
           x = as.Date("2021-12-01"), 
           y = 24,
           label = "Leaf Blight Percent Incidences \n May 2020 - July 2023",
           color = "chocolate4", size = 5, fill = "floralwhite") +  
  geom_line(aes(y = blight_forecast_percent_incidence),
            color = "firebrick", alpha = 3, size = 2) +
  annotate("text",
           x = as.Date("2024-09-01"), 
           y = 35,
           label = "Leaf Blight Forecast Incidences \n Aug 2023 - July 2025",
           color = "brown4", size = 5) +
  geom_ribbon(aes(ymin = 0, 
                  ymax = blight_up_mean),
              alpha = 0.1,
              fill = "orangered") +
  scale_y_continuous(
    breaks = seq(0, 56, 1.7)) +
  labs(x = "Planting Months",
       y = "Leaf Blight Percent Incidences",
       title = "Leaf Blight Percent Incidences and Forecast") +
  
  scale_x_date(date_labels = format("%b-%Y"),
               date_breaks = "1 month",
               limits = c(min(months_break), max(months_break))) +
  theme(
    plot.title.position = "panel",
    plot.title = element_text(margin = margin(0.1, 0.2, 1.2, 0.2, "cm"),
                              hjust = 0.5,
                              vjust = -119,
                              size = plot_title_size + 5),
    plot.margin = margin(0, 0.1, 1.22, 0.2, "cm"),
    aspect.ratio = 0.36,
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "gray96"),
    axis.text.y = element_text(size = 10,
                               color = "black",
                               face = "plain",
                               vjust = 0.25,
                               margin = margin(b = 1)), 
    axis.text.x = element_text(margin = margin(b = 1),
                               angle = 90, 
                               vjust = 0.5, 
                               size = 12),
    axis.title = element_text(margin = margin(t = 1.3),
                              size = 14)
  )
ggsave("Leaf Blight SARIMA Data and Forecast.png", 
       dpi = 150, height = 6, width = 12)
```

```Brown Spot Forecasting ARIMA``
```{r}
adf.test(brown_ts_data, alternative = "stationary", k=0)

brown_auto_arima_model <- 
  auto.arima(brown_ts_data, 
             d = 1, 
             D = 0,
             stepwise = FALSE,
             approximation = FALSE)
print(summary(brown_auto_arima_model))
checkresiduals(brown_auto_arima_model)


brown_forecast <- forecast(brown_auto_arima_model, 
                              level = c(95),
                              h = 2 * 12)

autoplot(brown_forecast, 
         y = "Brown Spot Percent Incidence", 
         x = "Years")


brown_df <- 
  tibble(
    months = months_vector,
    brown_percent_incidence = array(brown_ts_data),
    brown_lo_mean = NULL,
    brown_up_mean = NULL
  )


brown_forecast_df <- 
  tibble(
    months = forecast_months_vector,
    brown_forecast_percent_incidence = brown_forecast$mean,
    brown_lo_mean = brown_forecast$lower[,"95%"],
    brown_up_mean = brown_forecast$upper[,"95%"]
  )

brown_arima_data <-
  brown_df %>% full_join(brown_forecast_df, by = c("months"))


# annotate("label", x = 24, y = 25,
#              label = "Brown Spot May 2020 - July 2023 Percent Incidences",
#              parse = TRUE) +
#     

brown_arima_data %>%
  ggplot(aes(x = months, y = brown_percent_incidence)) +
  geom_line(color = "chartreuse3", alpha = 2, size = 2) +
  annotate("label",
           x = as.Date("2021-12-01"), 
           y = 24,
           label = "Brown Spot Percent Incidences \n May 2020 - July 2023",
           color = "darkolivegreen", size = 5, fill = "floralwhite") + 
  geom_line(aes(y = brown_forecast_percent_incidence),
            color = "lightseagreen", alpha = 3, size = 2.2) +
  annotate("text",
           x = as.Date("2024-09-01"), 
           y = 33,
           label = "Brown Spot Forecast Incidences \n Aug 2023 - July 2025",
           color = "forestgreen", size = 5)+
  geom_ribbon(aes(ymin = 0, 
                  ymax = brown_up_mean),
              alpha = 0.1,
              fill = "darkolivegreen1") +
  scale_y_continuous(
    breaks = seq(0, 42, 1.75)) +
  labs(x = "Planting Months",
       y = "Brown Spot Percent Incidences",
       title = "Brown Spot Percent Incidences and Forecast") +
  
  scale_x_date(date_labels = format("%b-%Y"),
               date_breaks = "1 month",
               limits = c(min(months_break), max(months_break))) +
  theme(
    plot.title.position = "panel",
    plot.title = element_text(margin = margin(0.1, 0.2, 1.2, 0.2, "cm"),
                              hjust = 0.5,
                              vjust = -119,
                              size = plot_title_size + 5),
    plot.margin = margin(0, 0.1, 1.22, 0.2, "cm"),
    aspect.ratio = 0.35,
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "gray96"),
    axis.text.y = element_text(size = 10,
                               color = "black",
                               face = "plain",
                               vjust = 0.25,
                               margin = margin(b = 1)), 
    axis.text.x = element_text(margin = margin(b = 1),
                               angle = 90, 
                               vjust = 0.5, 
                               size = 12),
    axis.title = element_text(margin = margin(t = 1.3),
                              size = 14)
  )
ggsave("Brown Spot SARIMA Data and Forecast.png", 
       dpi = 150, height = 6, width = 12)
```

```BLSB Forecasting ARIMA``
```{r}
adf.test(blsb_ts_data, alternative = "stationary", k=0)

blsb_auto_arima_model <- 
  auto.arima(blsb_ts_data, 
             d = 1,
             D = 0,
             stepwise = FALSE,
             approximation = FALSE)
print(summary(blsb_auto_arima_model))
checkresiduals(blsb_auto_arima_model)


blsb_forecast <- forecast(blsb_auto_arima_model, 
                             level = c(95),
                             h = 2 * 12)

autoplot(blsb_forecast, 
         y = "Banded Leaf and Sheath Blight Percent Incidence", 
         x = "Years")


blsb_df <- 
  tibble(
    months = months_vector,
    blsb_percent_incidence = array(blsb_ts_data),
    blsb_lo_mean = NULL,
    blsb_up_mean = NULL
  )


blsb_forecast_df <- 
  tibble(
    months = forecast_months_vector,
    blsb_forecast_percent_incidence = blsb_forecast$mean,
    blsb_lo_mean = blsb_forecast$lower[,"95%"],
    blsb_up_mean = blsb_forecast$upper[,"95%"]
  )

blsb_arima_data <-
  blsb_df %>% full_join(blsb_forecast_df, by = c("months"))


blsb_arima_data %>%
  ggplot(aes(x = months, y = blsb_percent_incidence)) +
  geom_line(color = "deepskyblue", alpha = 2, size = 2.2) +
  annotate("label",
           x = as.Date("2021-12-01"), 
           y = 24,
           label = "BLSB Percent Incidences \n May 2020 - July 2023",
           color = "dodgerblue4", size = 5, fill = "floralwhite") + 
  geom_line(aes(y = blsb_forecast_percent_incidence),
            color = "navyblue", alpha = 3, size = 2.2) +
  annotate("text",
           x = as.Date("2024-09-01"), 
           y = 24,
           label = "BLSB Forecast Incidences \n Aug 2023 - July 2025",
           color = "navyblue", size = 5) +
  geom_ribbon(aes(ymin = 0, 
                  ymax = blsb_up_mean),
              alpha = 0.1,
              fill = "lightskyblue1") +
  scale_y_continuous(
    breaks = seq(0, 34, 1.25)) +
  labs(x = "Planting Months",
       y = "Banded Leaf and Sheath Blight Percent Incidences",
       title = "Banded Leaf and Sheath Blight Percent Incidences and Forecast") +
  
  scale_x_date(date_labels = format("%b-%Y"),
               date_breaks = "1 month",
               limits = c(min(months_break), max(months_break))) +
  theme(
    plot.title.position = "panel",
    plot.title = element_text(margin = margin(0.1, 0.2, 1.2, 0.2, "cm"),
                              hjust = 0.5,
                              vjust = -119,
                              size = plot_title_size + 5),
    plot.margin = margin(0, 0.1, 1.22, 0.2, "cm"),
    aspect.ratio = 0.35,
    strip.background = element_blank(),
    strip.placement = "outside",
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "gray96"),
    axis.text.y = element_text(size = 10,
                               color = "black",
                               face = "plain",
                               vjust = 0.25,
                               margin = margin(b = 1)), 
    axis.text.x = element_text(margin = margin(b = 1),
                               angle = 90, 
                               vjust = 0.5, 
                               size = 12),
    axis.title = element_text(margin = margin(t = 1.3),
                              size = 14)
  )
ggsave("Banded Leaf and Sheath Blight SARIMA Data and Forecast.png", 
       dpi = 150, height = 6, width = 12)
```










