---
title: "disease_forecast"
author: "Mihkail Cornell"
date: "-12-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fpp2)
library(ggplot2)
library(stats)
library(tseries)
library(lubridate)
library(tidymodels)
library(scales)
library(forcats)
library(dplyr)
library(datawizard)

diseases_percent_incidence_with_weather_data <- 
  read_csv("monthly_disease_prcnt_inc_with_weather_data.csv")
```

```By Corn Type Top 3 Diseases```
```{r}
diseases_labels <- c("Banded Leaf and Sheath Blight" = "BLSB",
                  "Leaf Blight" = "Leaf Blight",
                  "Brown Spot" = "Brown Spot"
                  )
disease_fills <- c(
            "Banded Leaf and Sheath Blight" = "chartreuse3",
            "Brown Spot"= "deepskyblue2",
            "Leaf Blight" = "chocolate2"
            )


summary_diseases_corntype_corntype_df <-
  diseases_percent_incidence_with_weather_data %>%
  select(`Corn Type`, 
         `Brown Spot`, 
         `Banded Leaf and Sheath Blight`, 
         `Leaf Blight`) %>%
  pivot_longer(-c(`Corn Type`), 
               names_to = "diseases", 
               values_to = "incidences") %>%
  group_by(`Corn Type`, diseases) %>%
  summarise(mean_disease_incidences = mean(incidences))




summary_diseases_corntype_corntype_df %>%
  ggplot(aes(fct_reorder(diseases,
                         mean_disease_incidences,
                         .desc = TRUE), 
             mean_disease_incidences,
             fill = diseases)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = round(mean_disease_incidences, 2)),
                size = 5, color = "black", nudge_y = -3) +
  facet_grid(~ `Corn Type`, 
             scales = "free_x", 
             # space = "free_x",
             switch = "x") +
  scale_x_discrete(labels = diseases_labels) +
  scale_fill_manual(values = disease_fills) +
  labs(title = "Disease Incidences on GM and Non-GM Corn Types",
       x = NULL,
       y = "Percent Incidences") +
  theme(
          plot.title.position = "panel",
          plot.title = element_text(margin = margin(b=12),
                                                    hjust = 0.5,
                                                    vjust = -98,
                                    size = plot_title_size + 2),
          plot.margin = margin(t = -10, l = 10, b = 30),
          aspect.ratio = 1,
          strip.background = element_blank(),
          strip.placement = "outside",
          axis.text = element_text(size = 12,
                                   color = "black",
                                   face = "plain",
                                   vjust = -0.75,
                                   margin = margin(b = 10)), 
          axis.title = element_text(size = 16),
          strip.text.x =  element_text(size = 14)
          )
ggsave("../Graphs_for_TERMINAL_Report/Summary of Disease Incidences on GM and Non-GM Corn.png", 
       dpi = 150, height = 5, width = 8)
```


```Plot for Monthly Humidity```
```{r}
monthly_weather_disease_data <- read_csv("monthly_disease_prcnt_inc_with_weather_data.csv")

color_diseases <- c("chartreuse3", "deepskyblue2", "chocolate2")
color_labels <- c("Banded Leaf and Sheath Blight",
                  "Brown Spot", 
                  "Leaf Blight")

monthly_diseases_percent_incidence_data <-
  monthly_weather_disease_data %>%
  dplyr::select("Banded Leaf and Sheath Blight", 
                 "Brown Spot",
                 "Leaf Blight",
                Year, Month, mean_temp, mean_humid, mean_rain, mean_wind)


monthly_diseases_humidity_pivot <-
  monthly_diseases_percent_incidence_data %>%
  select("Banded Leaf and Sheath Blight", 
         "Brown Spot",
         "Leaf Blight",
         Year, Month, mean_humid) %>%
  pivot_longer(c("Banded Leaf and Sheath Blight", 
                 "Brown Spot",
                 "Leaf Blight"), 
               values_to = "incidence", 
               names_to = "diseases") %>%
  mutate(time_period = paste(Year, Month, sep = "-"),
         time_period = ym(time_period)) %>%
  ungroup() %>%
  select(-Year, -Month)


monthly_diseases_humidity_pivot %>% 
  ggplot(aes(x = time_period, 
             y = incidence,
             order = mean_humid)) +
    scale_y_continuous(
               breaks = seq(0, 80, 1.75),
               sec.axis = sec_axis(~. , name = "Monthly Humidity")) +
    geom_line(aes(time_period, 
                  incidence, 
                  color = diseases),
              linewidth = linewidth - 0.2,
              position = position_dodge(1)) +
    scale_x_date(date_labels = format("%b-%Y"),
                 date_breaks = "1 month" ,
                 breaks = month.breaks.vec) +
    geom_line(aes(y = mean_humid,
                  alpha = 0.9),
                  linewidth = linewidth,
                  show.legend = FALSE) +
    geom_area(aes(fill = mean_humid),
                  alpha = 0.3,
                  show.legend = FALSE,
                  position = "identity",
                  fill = "gray") +
    labs(y = "Percent Incidence",
         x = "Cropping Months",
         title = "Mean Monthly Disease Incidences and Mean Humidity from May 2020 - Aug 2023",
         caption = "*Monthly average humidity is in GRAY") +
    scale_color_manual(values = color_diseases) +
    theme(
          plot.title.position = "panel",
          plot.title = element_text(margin = margin(t=14),
                                    hjust = 0.5,
                                    vjust = -126,
                                    size = plot_title_size + 6),
          plot.margin = margin(-0.8,1,1.5,1.2, "cm"),
          plot.caption = element_text(hjust = 0.88),
          panel.background = element_rect(fill = NA),
          panel.grid.major = element_line(colour = "gray95"), 
          axis.text.x = element_text(margin = margin(b = 10),
                                     angle = 90, 
                                     vjust = 0.5, 
                                     size = axis_text_size + 2),
          axis.ticks = element_blank(),
          axis.text.y = element_text(margin = margin(b = 8, l = 4),
                                     vjust = 1, 
                                     hjust = 1, 
                                     size = axis_text_size),
          axis.title = element_text(size = title_text_size, face="bold",
                                    margin = margin(t = 13)),
          axis.ticks.y = element_blank(),
          legend.title = element_blank(),
          legend.position = c(0.6, 0.6), 
          legend.justification = c(0.2, 1.1), 
          legend.background = element_rect(fill = NA, colour = NA)
          )
ggsave("Summary of Monthly Mean Disease Incidences and Mean Humidity from May 2020 - Aug 2023.png", 
       dpi = 150, height = 8, width = 12)

```

```Plot for Monthly Temperature```
```{r}
plot_title_size <- 18
title_text_size <- 16
axis_text_size <- 13

monthly_diseases_temperature_pivot <-
  monthly_diseases_percent_incidence_data %>%
  select("Banded Leaf and Sheath Blight", 
         "Brown Spot",
         "Leaf Blight",
         Year, Month, mean_temp) %>%
  pivot_longer(c("Banded Leaf and Sheath Blight", 
                 "Brown Spot",
                 "Leaf Blight"), 
               values_to = "incidence", 
               names_to = "diseases") %>%
  mutate(time_period = paste(Year, Month, sep = "-"),
         time_period = ym(time_period)) %>%
  ungroup() %>%
  select(-Year, -Month)

monthly_diseases_temperature_pivot  %>%
    ggplot(aes(x = time_period, 
               y = incidence,
               order = mean_temp)) +
    scale_y_continuous(limits = c(0, 35),
               breaks = seq(0, 35, 0.85),
               sec.axis = sec_axis(~. , name = "Monthly Temperature")) +
    geom_line(aes(time_period, 
                  incidence, 
                  color = diseases),
                  linewidth = linewidth,
                  position = position_dodge(1)) +
    scale_x_date(date_labels = format("%b-%Y"),
                 date_breaks = "1 month",
                 limits = c(myd("May-2020"), my("Aug-2023"))) +
    geom_line(aes(y = mean_temp,
                  alpha = 0.9),
                  linewidth = linewidth,
                  show.legend = FALSE) +
    geom_area(alpha = 0.3,
              show.legend = FALSE,
              position = "identity",
              fill = "gray") +
    labs(y = "Percent Incidences",
         x = "Cropping Months",
         title = "Mean Monthly Disease Incidences and Mean Temperature from May 2020 - Aug 2023",
         caption = "*Monthly average temperature is in GRAY") +
    scale_color_manual(values = color_diseases) +
    theme(
          plot.title.position = "panel",
          plot.title = element_text(margin = margin(t=14),
                                    hjust = 0.5,
                                    vjust = -124,
                                    size = plot_title_size + 4),
          plot.margin = margin(-0.8,1.2,1.6,1.2, "cm"),
          plot.caption = element_text(hjust = 0.88),
          panel.background = element_rect(fill = NA),
          panel.grid.major = element_line(colour = "gray95"), 
          axis.text.x = element_text(margin = margin(b = 10),
                                     angle = 90, 
                                     vjust = 0.5, 
                                     size = axis_text_size + 2),
          axis.ticks = element_blank(),
          axis.text.y = element_text(margin = margin(b = 8, l = 4),
                                     vjust = 1.1, 
                                     hjust = 1, 
                                     size = axis_text_size - 0.4),
          axis.title = element_text(size = title_text_size, face="bold",
                                    margin = margin(t = 13)),
          axis.ticks.y = element_blank(),
          legend.title = element_blank(),
          legend.position = c(0.6, 0.6), 
          legend.justification = c(0.2, 1.1), 
          legend.background = element_rect(fill = NA, colour = NA)
          )
ggsave("Summary of Monthly Disease Incidences and Mean Temperature from May 2020 - Aug 2023.png", 
       dpi = 150, width = 12, height = 8)


```

```Plot for Monthly Rainfall```
```{r}
plot_title_size <- 16
title_text_size <- 15
axis_text_size <- 12

monthly_diseases_rainfall_pivot <-
  monthly_diseases_percent_incidence_data %>%
  select("Banded Leaf and Sheath Blight", 
         "Brown Spot",
         "Leaf Blight",
         Year, Month, mean_rain) %>%
  pivot_longer(c("Banded Leaf and Sheath Blight", 
                 "Brown Spot",
                 "Leaf Blight"), 
               values_to = "incidence", 
               names_to = "diseases") %>%
  mutate(time_period = paste(Year, Month, sep = "-"),
         time_period = ym(time_period)) %>%
  ungroup() %>%
  select(-Year, -Month)

monthly_diseases_rainfall_pivot  %>%
    ggplot(aes(x = time_period, 
               y = incidence,
               order = mean_rain)) +
    scale_y_continuous(limits = c(0, 35),
               breaks = seq(0, 35, 0.85),
               sec.axis = sec_axis(~. , name = "Monthly Rainfall")) +
    geom_line(aes(time_period, 
                  incidence, 
                  color = diseases),
                  linewidth = linewidth,
                  position = position_dodge(1)) +
    scale_x_date(date_labels = format("%b-%Y"),
                 date_breaks = "1 month",
                 limits = c(myd("May-2020"), my("Aug-2023"))) +
    geom_line(aes(y = mean_rain,
                  alpha = 0.9),
                  linewidth = linewidth,
                  show.legend = FALSE) +
    geom_area(alpha = 0.3,
              show.legend = FALSE,
              position = "identity",
              fill = "gray") +
    labs(y = "Percent Incidences",
         x = "Cropping Months",
         title = "Mean Monthly Disease Incidences and Mean Rainfall from May 2020 - Aug 2023",
         caption = "*Monthly average rainfall is in GRAY") +
    scale_color_manual(values = color_diseases) +
    theme(
          plot.title.position = "panel",
          plot.title = element_text(margin = margin(t=14),
                                    hjust = 0.5,
                                    vjust = -140,
                                    size = plot_title_size + 4),
          plot.margin = margin(-0.8,1.2,1.6,1.2, "cm"),
          plot.caption = element_text(hjust = 0.88),
          panel.background = element_rect(fill = NA),
          panel.grid.major = element_line(colour = "gray95"), 
          axis.text.x = element_text(margin = margin(b = 10),
                                     angle = 90, 
                                     vjust = 0.5, 
                                     size = axis_text_size + 2),
          axis.ticks = element_blank(),
          axis.text.y = element_text(margin = margin(b = 8, l = 4),
                                     vjust = 1.1, 
                                     hjust = 1, 
                                     size = axis_text_size - 0.4),
          axis.title = element_text(size = title_text_size, face="bold",
                                    margin = margin(t = 13)),
          axis.ticks.y = element_blank(),
          legend.title = element_blank(),
          legend.position = c(0.6, 0.6), 
          legend.justification = c(0.2, 1.1), 
          legend.background = element_rect(fill = NA, colour = NA)
          )
ggsave("Summary of Monthly Disease Incidences and Mean Rainfall from May 2020 - Aug 2023.png", 
       dpi = 150, width = 12, height = 8)


```

```Plot for Monthly Wind Speed```
```{r}
plot_title_size <- 16
title_text_size <- 15
axis_text_size <- 12

monthly_diseases_windspeed_pivot <-
  monthly_diseases_percent_incidence_data %>%
  select("Banded Leaf and Sheath Blight", 
         "Brown Spot",
         "Leaf Blight",
         Year, Month, mean_wind) %>%
  pivot_longer(c("Banded Leaf and Sheath Blight", 
                 "Brown Spot",
                 "Leaf Blight"), 
               values_to = "incidence", 
               names_to = "diseases") %>%
  mutate(time_period = paste(Year, Month, sep = "-"),
         time_period = ym(time_period)) %>%
  ungroup() %>%
  select(-Year, -Month)

monthly_diseases_windspeed_pivot  %>%
    ggplot(aes(x = time_period, 
               y = incidence,
               order = mean_wind)) +
    scale_y_continuous(limits = c(0, 35),
               breaks = seq(0, 35, 0.85),
               sec.axis = sec_axis(~. , name = "Monthly Wind Speed")) +
    geom_line(aes(time_period, 
                  incidence, 
                  color = diseases),
                  linewidth = linewidth,
                  position = position_dodge(1)) +
    scale_x_date(date_labels = format("%b-%Y"),
                 date_breaks = "1 month",
                 limits = c(myd("May-2020"), my("Aug-2023"))) +
    geom_line(aes(y = mean_wind,
                  alpha = 0.9),
                  linewidth = linewidth,
                  show.legend = FALSE) +
    geom_area(alpha = 0.3,
              show.legend = FALSE,
              position = "identity",
              fill = "gray") +
    labs(y = "Percent Incidences",
         x = "Cropping Months",
         title = "Mean Monthly Disease Incidences and Mean Wind Speed from May 2020 - Aug 2023",
         caption = "*Monthly average wind speed is in GRAY") +
    scale_color_manual(values = color_diseases) +
    theme(
          plot.title.position = "panel",
          plot.title = element_text(margin = margin(t=14),
                                    hjust = 0.5,
                                    vjust = -140,
                                    size = plot_title_size + 4),
          plot.margin = margin(-0.8,1.2,1.6,1.2, "cm"),
          plot.caption = element_text(hjust = 0.88),
          panel.background = element_rect(fill = NA),
          panel.grid.major = element_line(colour = "gray95"), 
          axis.text.x = element_text(margin = margin(b = 10),
                                     angle = 90, 
                                     vjust = 0.5, 
                                     size = axis_text_size + 2),
          axis.ticks = element_blank(),
          axis.text.y = element_text(margin = margin(b = 8, l = 4),
                                     vjust = 1.1, 
                                     hjust = 1, 
                                     size = axis_text_size - 0.4),
          axis.title = element_text(size = title_text_size, face="bold",
                                    margin = margin(t = 13)),
          axis.ticks.y = element_blank(),
          legend.title = element_blank(),
          legend.position = c(0.6, 0.6), 
          legend.justification = c(0.2, 1.1), 
          legend.background = element_rect(fill = NA, colour = NA)
          )
ggsave("Summary of Monthly Disease Incidences and Mean Wind Speed from May 2020 - Aug 2023.png", 
       dpi = 150, width = 12, height = 8)


```

``` Heatmap Corn Type - Crop Stage```
```{r}
diseases_summary_overall <- diseases_prcnt_inc_df


color_diseases <- c("chartreuse3", "deepskyblue2", "chocolate2")
color_labels <- c("Banded Leaf and Sheath Blight",
                  "Brown Spot", 
                  "Leaf Blight")

color_diseases <- c("deepskyblue2", "chartreuse3", "chocolate2")

growth_stage <- c("Emergence", "Single Leaf", "Seedling (3 - 4 Leaves)",
                  "Early Whorl", "Mid Whorl", "Late Whorl",
                  "Tasseling", "Silking", "Maturity")

summary_diseases_province_corntype_df <-
  diseases_summary_overall %>%
  select(`Crop Stage`, `Corn Type`, 
         `Brown Spot`, 
         `Banded Leaf and Sheath Blight`, 
         `Leaf Blight`) %>%
  pivot_longer(-c(`Crop Stage`, `Corn Type`), 
               names_to = "diseases", 
               values_to = "incidences") %>%
  group_by(`Crop Stage`, `Corn Type`, diseases) %>%
  summarise(mean_disease_incidences = mean(incidences))



# brown
summary_diseases_province_corntype_df %>%
  dplyr::filter(diseases == "Brown Spot") %>%
  ggplot(aes(x = factor(`Crop Stage`, level = growth_stage), 
             y = factor(`Corn Type`, level = c("Non - GM Corn", "GM CORN")),
             fill = mean_disease_incidences,
             group = diseases)) + 
  geom_tile() +
  scale_fill_gradient(low = "white", high = "chartreuse3") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  geom_text(aes(label = round(mean_disease_incidences, 2)), 
            color = "black", size = 5) +
  labs(x = "Crop Stages",
       y = "Corn Types",
       fill = "Brown Spot Mean \nPercent Incidence",
       title = "Heatmap of Brown Spot Percent Incidence on Corn Types and Crop Stages") +
  theme(
        plot.margin = unit(c(0, 0, 2, 1), "cm"),
        plot.title.position = "panel",
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(margin = margin(b = -20),
                                  hjust = 0.5,
                                  vjust = -75,
                                  size = 20),
        axis.title = element_text(size = 14,
                                  vjust = -1.8,
                                  margin = margin(t = 25, b = 15)),
        axis.text = element_text(color = "black",
                                 face = "plain",
                                 vjust = -0.75,
                                 size = 9,
                                 margin = margin(b = 8)),
        axis.ticks.length=unit(.25, "cm")
  )
ggsave("Corn Types and Crop Stage Heat map Brown Spot.png", dpi = 150, width = 10)


# blsb
summary_diseases_province_corntype_df %>%
  dplyr::filter(diseases == "Banded Leaf and Sheath Blight",
         `Crop Stage` != "Emergence") %>%
  ggplot(aes(x = factor(`Crop Stage`, level = growth_stage), 
             y = factor(`Corn Type`, level = c("Non - GM Corn", "GM CORN")),
             fill = mean_disease_incidences,
             group = diseases)) + 
  geom_tile() +
  scale_fill_gradient(low = "white", high = "deepskyblue2") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  geom_text(aes(label = round(mean_disease_incidences, 2)), 
            color = "black", size = 5) +
  labs(x = "Crop Stages",
       y = "Corn Types",
       fill = "BLSB Mean \nPercent Incidence",
       title = "Heatmap of BLSB Percent Incidence on Corn Types and Crop Stages") +
  theme(
        plot.margin = unit(c(0, 0, 2, 1), "cm"),
        plot.title.position = "panel",
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(margin = margin(b = -20),
                                  hjust = 0.5,
                                  vjust = -75,
                                  size = 20),
        axis.title = element_text(size = 14,
                                  vjust = -1.8,
                                  margin = margin(t = 25, b = 15)),
        axis.text = element_text(color = "black",
                                 face = "plain",
                                 vjust = -0.75,
                                 size = 9,
                                 margin = margin(b = 8)),
        axis.ticks.length=unit(.25, "cm")
  )
ggsave("Corn Types and Crop Stage Heat map BLSB.png", dpi = 150, width = 10)


# Leaf Blight
summary_diseases_province_corntype_df %>%
  dplyr::filter(diseases == "Leaf Blight",
         `Crop Stage` != "Emergence") %>%
  ggplot(aes(x = factor(`Crop Stage`, level = growth_stage), 
             y = factor(`Corn Type`, level = c("Non - GM Corn", "GM CORN")),
             fill = mean_disease_incidences,
             group = diseases)) + 
  geom_tile() +
  scale_fill_gradient(low = "white", high = "chocolate2") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  geom_text(aes(label = round(mean_disease_incidences, 2)), 
            color = "black", size = 5) +
  labs(x = "Crop Stages",
       y = "Corn Types",
       fill = "Leaf Blight Mean \nPercent Incidence",
       title = "Heatmap of Leaf Blight Percent Incidence on Corn Types and Crop Stages") +
  theme(
        plot.margin = unit(c(0, 0, 2, 1), "cm"),
        plot.title.position = "panel",
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(margin = margin(b = -20),
                                  hjust = 0.5,
                                  vjust = -75,
                                  size = 20),
        axis.title = element_text(size = 14,
                                  vjust = -1.8,
                                  margin = margin(t = 25, b = 15)),
        axis.text = element_text(color = "black",
                                 face = "plain",
                                 vjust = -0.75,
                                 size = 9,
                                 margin = margin(b = 8)),
        axis.ticks.length=unit(.25, "cm")
  )
ggsave("Corn Types and Crop Stage Heat map Leaf Blight.png", dpi = 150, width = 10)
```


```Monthly Averages Graph```
```{r setup, fig.width = 12, fig.height = 7}
line_size <- 2

diseases <- c("BLSB", "Common Rust", "Southern Rust", "Leaf Blight", 
              "Brown Spot", "Leaf Spot", "Leaf Blight", "Stalk Rot")

disease_colors <- c("blsb" = "blueviolet",
                    "rust" = "mediumvioletred",
                    "southrust" = "olivedrab",
                    "mildew" ="orange3",
                    `brown` = "palevioletred1",
                    "leaf" = "deepskyblue",
                    "blight" = "gray37",
                    "stalk" = "tomato4"
                    )

diseases_monthly_average_df %>%
    pivot_longer(cols = !month, 
                 values_to = "monthly_incidence", 
                 names_to = "disease_incidence") %>%
    ggplot(aes(month, monthly_incidence, color = disease_incidence)) +
    geom_line(size = line_size) +
    scale_x_date(date_labels = format("%b-%Y"),
                 date_breaks = "1 month") +
    scale_color_manual(values = disease_colors, labels = diseases) +
    # facet_grid(. ~ year(ymd(month)), scale = "free_x") +
    # scale_x_yearmonth(date_labels = "%Y",
    #                   date_breaks = "1 year") +
    theme(axis.text.x = element_text(angle = 90, 
                                     vjust = 0.5, 
                                     hjust = 0.5,
                                     size = 14),
          axis.text.y = element_text(vjust = 0.5, 
                                     size = 16, 
                                      margin = margin(t = 0, r = 10, b = 0, l = 10)),
          axis.title.x = element_text(size = 16, 
                                      margin = margin(t = 10, r = 20, b = 0, l = 0)),
          axis.title.y = element_text(size = 15),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 15)) +
    labs(x = "Time Period (May 2020 - Aug 2023)",
         y = "Average Monthly diseases Percent Incidence",
         color = "diseases") 
```




```Monthly and by Crop Stage Averages```
```{r}
blsb_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_blsb) %>%
  ggplot(aes(collect_date, incidence_blsb)) +
  geom_smooth()


blsb_ts_df <- blsb_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_blsb) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_blsb, `Crop Stage`, month = floor_date(Date, "month")) %>%
  group_by(month, `Crop Stage`) %>%
  summarise(blsb_monthly_average_incidence = mean(incidence_blsb)) 

blsb_ts_df <-
  blsb_ts_df %>% 
  replace(is.na(blsb_ts_df), mean(blsb_ts_df$blsb_monthly_average_incidence, na.rm = TRUE))


rust_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_rust) %>%
  ggplot(aes(collect_date, incidence_rust)) +
  geom_smooth()


rust_ts_df <- rust_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_rust) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_rust, `Crop Stage`, month = floor_date(Date, "month")) %>%
  group_by(month, `Crop Stage`) %>%
  summarise(rust_monthly_average_incidence = mean(incidence_rust)) 

rust_ts_df <-
  rust_ts_df %>% 
  replace(is.na(rust_ts_df), 
          mean(rust_ts_df$rust_monthly_average_incidence, na.rm = TRUE))

southrust_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_southrust) %>%
  ggplot(aes(collect_date, incidence_southrust)) +
  geom_smooth()


southrust_ts_df <- southrust_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_southrust) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_southrust, `Crop Stage`, month = floor_date(Date, "month")) %>%
  group_by(month, `Crop Stage`) %>%
  summarise(southrust_monthly_average_incidence = mean(incidence_southrust)) 

southrust_ts_df <-
  southrust_ts_df %>% 
  replace(is.na(southrust_ts_df), mean(southrust_ts_df$southrust_monthly_average_incidence, na.rm = TRUE))

mildew_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_mildew) %>%
  ggplot(aes(collect_date, incidence_mildew)) +
  geom_smooth()


mildew_ts_df <- mildew_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_mildew) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_mildew, `Crop Stage`, month = floor_date(Date, "month")) %>%
  group_by(month, `Crop Stage`) %>%
  summarise(mildew_monthly_average_incidence = mean(incidence_mildew)) 

mildew_ts_df <-
  mildew_ts_df %>% 
  replace(is.na(mildew_ts_df), mean(mildew_ts_df$mildew_monthly_average_incidence, na.rm = TRUE))

brown_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_brown) %>%
  ggplot(aes(collect_date, incidence_brown)) +
  geom_smooth()


brown_ts_df <- brown_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_brown) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_brown, `Crop Stage`, month = floor_date(Date, "month")) %>%
  group_by(month, `Crop Stage`) %>%
  summarise(brown_monthly_average_incidence = mean(incidence_brown)) 

brown_ts_df <-
  brown_ts_df %>% 
  replace(is.na(brown_ts_df), mean(brown_ts_df$brown_monthly_average_incidence, na.rm = TRUE))


leaf_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_leaf) %>%
  ggplot(aes(collect_date, incidence_leaf)) +
  geom_smooth()


leaf_ts_df <- leaf_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_leaf) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_leaf, `Crop Stage`, month = floor_date(Date, "month")) %>%
  group_by(month, `Crop Stage`) %>%
  summarise(leaf_monthly_average_incidence = mean(incidence_leaf)) 

leaf_ts_df <-
  leaf_ts_df %>% 
  replace(is.na(leaf_ts_df), mean(leaf_ts_df$leaf_monthly_average_incidence, na.rm = TRUE))

blight_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_blight) %>%
  ggplot(aes(collect_date, incidence_blight)) +
  geom_smooth()


blight_ts_df <- blight_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_blight) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_blight, `Crop Stage`, month = floor_date(Date, "month")) %>%
  group_by(month, `Crop Stage`) %>%
  summarise(blight_monthly_average_incidence = mean(incidence_blight)) 

blight_ts_df <-
  blight_ts_df %>% 
  replace(is.na(blight_ts_df), mean(blight_ts_df$blight_monthly_average_incidence, na.rm = TRUE))

stalk_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_stalk) %>%
  ggplot(aes(collect_date, incidence_stalk)) +
  geom_smooth()


stalk_ts_df <- stalk_joined_ev %>%
  select(collect_date, `Crop Stage`, incidence_stalk) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_stalk, `Crop Stage`, month = floor_date(Date, "month")) %>%
  group_by(month, `Crop Stage`) %>%
  summarise(stalk_monthly_average_incidence = mean(incidence_stalk)) 

stalk_ts_df <-
  stalk_ts_df %>% 
  replace(is.na(stalk_ts_df), mean(stalk_ts_df$stalk_monthly_average_incidence, na.rm = TRUE))


diseases_ts_df <-
  blsb_ts_df %>%
  full_join(rust_ts_df) %>%
  full_join(southrust_ts_df) %>%
  full_join(mildew_ts_df) %>%
  full_join(brown_ts_df) %>%
  full_join(leaf_ts_df) %>%
  full_join(blight_ts_df) %>%
  full_join(stalk_ts_df)
```


```By cropping``
```{r}
#arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)
crop_growth_stages_monthly <- c("Emergence", "Single Leaf", 
                                "Seedling (3 - 4 Leaves)", 
                                "Early Whorl", "Mid Whorl", 
                                "Late Whorl", "Tasseling", 
                                "Silking", "Maturity")

# first cropping 2020
diseases_1stcrop_2020 <-
  diseases_ts_df %>%
  filter(year(ymd(month)) == "2020") %>% 
  group_by(month, `Crop Stage`) %>%
  arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))

# 2nd cropping 2021
diseases_2ndcrop_2021_july <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2021",
           month(ymd(month)) == 7, 
           `Crop Stage` %in% c("Late Whorl", "Tasseling", 
                                "Silking", "Maturity"))

diseases_2ndcrop_2021 <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2021", month(ymd(month)) %in% seq(1, 7)) %>% 
    group_by(month, `Crop Stage`) %>%
    ungroup() %>% 
    arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  full_join(diseases_2ndcrop_2021_july)



# 3rd cropping 2021 - 2022
diseases_3rdcrop_2021_july <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2021",
           month(ymd(month)) == 7, 
           `Crop Stage` %in% c("Single Leaf", 
                                "Seedling (3 - 4 Leaves)", 
                                "Early Whorl", "Mid Whorl"))
diseases_3rdcrop_2022_january <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2022" & month(ymd(month)) == 1)

diseases_3rdcrop_2021 <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2021" & month(ymd(month)) %in% seq(7, 9)) %>% 
    group_by(month, `Crop Stage`) %>%
    arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
    full_join(diseases_3rdcrop_2021_july) %>%
    full_join(diseases_3rdcrop_2022_january)



# 4th cropping 2022
diseases_4thcrop_2022_may <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2022",
           month(ymd(month)) == 5, 
           `Crop Stage` %in% c("Late Whorl", "Tasseling", 
                                "Silking", "Maturity"))

diseases_4thcrop_2022 <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2022", month(ymd(month)) %in% seq(2, 4)) %>% 
    group_by(month, `Crop Stage`) %>%
    arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  full_join(diseases_4thcrop_2022_may)



# 5th cropping 2022
diseases_5thcrop_2022_may <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2022",
           month(ymd(month)) %in% c(4, 5),
           `Crop Stage` %in% c("Single Leaf", 
                                "Seedling (3 - 4 Leaves)", 
                                "Early Whorl", "Mid Whorl"))

diseases_5thcrop_2023_january <-
  diseases_ts_df %>%
     filter(year(ymd(month)) == "2023",
            month(ymd(month)) %in% c(1, 2, 3), 
           `Crop Stage` %in% c("Late Whorl", "Tasseling", 
                                "Silking", "Maturity"))

diseases_5thcrop_2022 <-
  diseases_5thcrop_2022_may %>% 
  full_join(
    diseases_ts_df %>%
        filter(
        year(ymd(month)) == "2022", 
        month(ymd(month)) %in% seq(6, 12)) %>% 
        group_by(month, `Crop Stage`) %>%
        arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))) %>%
  full_join(diseases_5thcrop_2023_january)







# 6th cropping 2023
diseases_6thcrop_2023_february <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2023",
           month(ymd(month)) %in% c(2, 3), 
           `Crop Stage` %in% c("Single Leaf", 
                                "Seedling (3 - 4 Leaves)", 
                                "Early Whorl", "Mid Whorl"))


diseases_6thcrop_2023 <-
  diseases_ts_df %>%
    filter(year(ymd(month)) == "2023", 
           month(ymd(month)) %in% seq(4, 12)) %>% 
    group_by(month, `Crop Stage`) %>%
    arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
    full_join(diseases_6thcrop_2023_february)
```

```{r}
# 1st plant
diseases_1stplant_2020 <- 
  diseases_ts_df %>%
    filter(month %in% c("2020-05-01"), 
                `Crop Stage` %in% c("Single Leaf", "Seedling (3 - 4 Leaves)", "Early Whorl")) %>%      full_join(
      diseases_ts_df %>% 
        filter(month %in% c("2020-06-01"),
                  `Crop Stage` == "Mid Whorl")) %>%
      full_join(
        diseases_ts_df %>% 
          filter(month %in% c("2020-07-01"), 
                `Crop Stage` %in% c("Late Whorl", "Tasseling", 
                                    "Silking", "Maturity")))



# 2nd plant
diseases_2ndplant_2020 <- 
  diseases_ts_df %>%
    filter(month %in% c("2020-06-01"), 
                `Crop Stage` %in% c("Single Leaf", "Seedling (3 - 4 Leaves)", "Early Whorl")) %>%      full_join(
      diseases_ts_df %>% 
        filter(month %in% c("2020-07-01"),
                  `Crop Stage` %in% c("Mid Whorl", "Late Whorl")) %>%
      full_join(
        diseases_ts_df %>% 
          filter(month %in% c("2020-07-01"), 
                `Crop Stage` %in% c("Late Whorl", "Tasseling", 
                                    "Silking", "Maturity")))
```


```{r}
diseases_ts_df %>% 
  filter(year(ymd(month)) == "2020") %>%
  arrange()

diseases_ts_df %>% 
  filter(year(ymd(month)) == "2021") %>%
  arrange()

diseases_ts_df %>% 
  filter(year(ymd(month)) == "2022") %>%
  arrange()

diseases_ts_df %>% 
  filter(year(ymd(month)) == "2023") %>%
  arrange()

# 2nd cropping 2020
diseases_2ndcrop_2020 <-
  diseases_ts_df %>%
  filter(year(ymd(month)) == "2020", month(ymd(month)) %in% c(6, 7, 8, 9),) %>% 
  group_by(month, `Crop Stage`) %>%
  # arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  ungroup() %>% 
  data_unique(`Crop Stage`, keep = "first") %>%
  arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))


# 3rd cropping 2020
diseases_3rdcrop_2020 <-
  diseases_ts_df %>%
  filter(year(ymd(month)) == "2020", month(ymd(month)) %in% c(8, 9, 10, 11)) %>% 
  group_by(month, `Crop Stage`) %>%
  # arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  ungroup() %>% 
  data_unique(`Crop Stage`, keep = "first") %>%
  arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))



# 4th cropping 2021
diseases_4thcrop_2021 <-
  diseases_ts_df %>%
  filter(year(ymd(month)) == "2021", month(ymd(month)) %in% c(1, 2, 3, 4, 5)) %>% 
  group_by(month, `Crop Stage`) %>%
  # arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  ungroup() %>% 
  data_unique(`Crop Stage`, keep = "first") %>%
  arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))


# 5th cropping 2021
diseases_5thcrop_2021 <-
  diseases_ts_df %>%
  filter(year(ymd(month)) == "2021", month(ymd(month)) %in% c(4, 5, 6, 7, 8)) %>% 
  group_by(month, `Crop Stage`) %>%
  # arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  ungroup() %>% 
  data_unique(`Crop Stage`, keep = "first") %>%
  arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))


# 6th cropping 2021
diseases_6thcrop_2021 <-
  diseases_ts_df %>%
  filter(year(ymd(month)) == "2021", month(ymd(month)) %in% c(9, 10, 11, 12)) %>% 
  group_by(month, `Crop Stage`) %>%
  # arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  ungroup() %>% 
  data_unique(`Crop Stage`, keep = "first") %>%
  arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))




# 7th cropping 2022
diseases_7thcrop_2022 <-
  diseases_ts_df %>%
  filter(year(ymd(month)) == "2022", month(ymd(month)) %in% c(2, 3, 4)) %>% 
  group_by(month, `Crop Stage`) %>%
  # arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  ungroup() %>% 
  data_unique(`Crop Stage`, keep = "first") %>%
  arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))


# 8th cropping 2021
diseases_8thcrop_2022 <-
  diseases_ts_df %>%
  filter(year(ymd(month)) == "2022", month(ymd(month)) %in% c(5, 6, 7, 8)) %>% 
  group_by(month, `Crop Stage`) %>%
  # arrange(month, match(`Crop Stage`, crop_growth_stages_monthly)) %>%
  ungroup() %>% 
  data_unique(`Crop Stage`, keep = "first") %>%
  arrange(month, match(`Crop Stage`, crop_growth_stages_monthly))
```



```Monthly Averages```
```{r}
blsb_joined_ev %>%
  select(collect_date, incidence_blsb) %>%
  ggplot(aes(collect_date, incidence_blsb)) +
  geom_smooth()


blsb_monthly_average_df <- blsb_joined_ev %>%
  select(collect_date, incidence_blsb) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_blsb, month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(blsb_monthly_average_incidence = mean(incidence_blsb)) 

blsb_monthly_average_df <-
  blsb_monthly_average_df %>% 
  replace(is.na(blsb_monthly_average_df), mean(blsb_monthly_average_df$blsb_monthly_average_incidence, na.rm = TRUE))


rust_joined_ev %>%
  select(collect_date, incidence_rust) %>%
  ggplot(aes(collect_date, incidence_rust)) +
  geom_smooth()


rust_monthly_average_df <- rust_joined_ev %>%
  select(collect_date, incidence_rust) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_rust, month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(rust_monthly_average_incidence = mean(incidence_rust)) 

rust_monthly_average_df <-
  rust_monthly_average_df %>% 
  replace(is.na(rust_monthly_average_df), 
          mean(rust_monthly_average_df$rust_monthly_average_incidence, na.rm = TRUE))

southrust_joined_ev %>%
  select(collect_date, incidence_southrust) %>%
  ggplot(aes(collect_date, incidence_southrust)) +
  geom_smooth()


southrust_monthly_average_df <- southrust_joined_ev %>%
  select(collect_date, incidence_southrust) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_southrust, month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(southrust_monthly_average_incidence = mean(incidence_southrust)) 

southrust_monthly_average_df <-
  southrust_monthly_average_df %>% 
  replace(is.na(southrust_monthly_average_df), mean(southrust_monthly_average_df$southrust_monthly_average_incidence, na.rm = TRUE))

mildew_joined_ev %>%
  select(collect_date, incidence_mildew) %>%
  ggplot(aes(collect_date, incidence_mildew)) +
  geom_smooth()


mildew_monthly_average_df <- mildew_joined_ev %>%
  select(collect_date, incidence_mildew) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_mildew, month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(mildew_monthly_average_incidence = mean(incidence_mildew)) 

mildew_monthly_average_df <-
  mildew_monthly_average_df %>% 
  replace(is.na(mildew_monthly_average_df), mean(mildew_monthly_average_df$mildew_monthly_average_incidence, na.rm = TRUE))

brown_joined_ev %>%
  select(collect_date, incidence_brown) %>%
  ggplot(aes(collect_date, incidence_brown)) +
  geom_smooth()


brown_monthly_average_df <- brown_joined_ev %>%
  select(collect_date, incidence_brown) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_brown, month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(brown_monthly_average_incidence = mean(incidence_brown)) 

brown_monthly_average_df <-
  brown_monthly_average_df %>% 
  replace(is.na(brown_monthly_average_df), mean(brown_monthly_average_df$brown_monthly_average_incidence, na.rm = TRUE))


leaf_joined_ev %>%
  select(collect_date, incidence_leaf) %>%
  ggplot(aes(collect_date, incidence_leaf)) +
  geom_smooth()


leaf_monthly_average_df <- leaf_joined_ev %>%
  select(collect_date, incidence_leaf) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_leaf, month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(leaf_monthly_average_incidence = mean(incidence_leaf)) 

leaf_monthly_average_df <-
  leaf_monthly_average_df %>% 
  replace(is.na(leaf_monthly_average_df), mean(leaf_monthly_average_df$leaf_monthly_average_incidence, na.rm = TRUE))

blight_joined_ev %>%
  select(collect_date, incidence_blight) %>%
  ggplot(aes(collect_date, incidence_blight)) +
  geom_smooth()


blight_monthly_average_df <- blight_joined_ev %>%
  select(collect_date, incidence_blight) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_blight, month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(blight_monthly_average_incidence = mean(incidence_blight)) 

blight_monthly_average_df <-
  blight_monthly_average_df %>% 
  replace(is.na(blight_monthly_average_df), mean(blight_monthly_average_df$blight_monthly_average_incidence, na.rm = TRUE))

stalk_joined_ev %>%
  select(collect_date, incidence_stalk) %>%
  ggplot(aes(collect_date, incidence_stalk)) +
  geom_smooth()


stalk_monthly_average_df <- stalk_joined_ev %>%
  select(collect_date, incidence_stalk) %>%
  mutate(Date = as.Date(collect_date, format = "%Y-%m-%d")) %>%
  group_by(incidence_stalk, month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(stalk_monthly_average_incidence = mean(incidence_stalk)) 

stalk_monthly_average_df <-
  stalk_monthly_average_df %>% 
  replace(is.na(stalk_monthly_average_df), mean(stalk_monthly_average_df$stalk_monthly_average_incidence, na.rm = TRUE))


diseases_monthly_average_df <-
  blsb_monthly_average_df %>%
  full_join(rust_monthly_average_df) %>%
  full_join(southrust_monthly_average_df) %>%
  full_join(mildew_monthly_average_df) %>%
  full_join(brown_monthly_average_df) %>%
  full_join(leaf_monthly_average_df) %>%
  full_join(blight_monthly_average_df) %>%
  full_join(stalk_monthly_average_df)
```


```{r setup, include=FALSE}
monthly_disease <- read.csv("../overall_summary/diseases_monthly_percent_incidence_averages_with_temp.csv")


monthly_disease_df <- 
  monthly_disease %>%
  select(brown, blsb, mildew, Year, Month, temperature) %>%
  mutate(time_period = paste(Year, Month, sep = "-"),
         time_period = ym(time_period),
         incidence_brown = brown,
         incidence_blsb = blsb,
         incidence_mildew = mildew) %>%
  ungroup()  %>% 
  select(-c(brown, blsb, mildew)) %>%
  pivot_longer(starts_with("incidence_"), names_to = "diseases", values_to = "incidence")


color_diseases <- c("brown" = "chocolate2", 
                  "blsb"= "deepskyblue2", 
                  "mildew" =   "chartreuse3")
```
